% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}
\usepackage[dvipsnames]{xcolor}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage{multicol}
\topmargin=-0.5in  % start text higher on the page
\begin{document}
\name{\textcolor{NavyBlue}{James Spears} - \textcolor{black}{\bf Software Developer} }

\begin{resume}

	\section{\textcolor{NavyBlue}{CONTACT INFO}}

	\normalsize{\section{Mailing Address}}
	{James Spears \\ Toronto, ON \\ (416) 827-3687}

	\normalsize{\section{Links}}
	\begin{itemize}
		\item \href{mailto:james.w.spears@gmail.com}{\textcolor{blue}{james.w.spears@gmail.com}}
		\item \href{https://github.com/jameone}{\textcolor{blue}{GitHub}} - \href{https://github.com/jameone/resume}{\textcolor{blue}{Fork this resume}}
		\item \href{https://www.linkedin.com/in/james-spears-50834b8a/}{\textcolor{blue}{LinkedIn}}
		\item \href{https://s3.amazonaws.com/james-spears.com/resume.docx}{\textcolor{blue}{MS Word format}}
	\end{itemize}

	\section{\textcolor{NavyBlue}{INTRO}}

	\normalsize{\section{About Me}}
	I enjoy working with software. I see myself fitting into the right organization
	as a software engineer or developer who spends their time iterating on the existing design
	and implementation of highly impactful software products. As my career progresses I would
	hope to play a larger role in the initial design and architecture of new and exciting products that
	push the boundaries of what was previously thought ``possible".

	My goal is to one day be owner/lead of a software product that is meaningful to users
	and that makes a positive impact on their day-to-day lives.

	\section{\textcolor{NavyBlue}{EDUCATION}}

	University of Waterloo, Waterloo, ON \\
	Bachelor of Science, General Science, \\
	commencement Fall 2018

	Durham College, Oshawa, ON \\
	Advanced Diploma, Electromechanical Engineering Technologist, \\
	commencement Fall 2011


	\section{\textcolor{NavyBlue}{EXPERIENCE}}

	\normalsize{\section{BMO Financial Group}}

	BMO Financial Group is a highly diversified financial services provider offering
	a broad range of personal and commercial banking, wealth management and investment
	banking products and services to 12 million customers through three operating groups.

	\begin{tabular}{p{3in} r} % setup 2 columns, first
		% is 3 inches wide
		UI Developer - \href{https://bmo.com}{\textcolor{blue}{BMO Financial Group (OLBB)}}, Toronto, ON & January 2022 - Present
	\end{tabular}

	\begin{itemize} % \item[] prevents a bullet from appearing
		\item Member of the Online Banking for Business team.
		\item Develop and maintain Angular front end applications. Work with TypeScript, JavaScript and Node.js on a daily basis.
		\item Code refactoring and Angular unit testing using Karma, and Jasmine.
		\item Implement user stories in an agile environment using tools such as Jira, Bitbucket, and Confluence.
	\end{itemize}

	\normalsize{\section{WebsiteBox}}

	WebsiteBox is a late stage startup offering website hosting and WYSIWYG
	website design to members of the real estate industry. Agents and brokers
	can have a good looking website that is also fully integrated with their
	MLS, up and running in minutes on WebsiteBox's PaaS.

	\begin{tabular}{p{3in} r} % setup 2 columns, first
		% is 3 inches wide
		Node.js Developer - \href{https://websitebox.com}{\textcolor{blue}{WebsiteBox}}, Toronto, ON & February 2021 - December 2021
	\end{tabular}

	\begin{itemize} % \item[] prevents a bullet from appearing
		\item Developed and maintained Angular \& AngularJS front end applications and supporting
		      express microservices. Worked with TypeScript, JavaScript and Node.js on a daily basis.
		      Implementing features in an agile environment using Jira, Bitbucket, and Confluence.
		      Modifying the JS tool chain (Babel, Gulp, Webpack) and CI/CD (Bitbucket, Docker) pipeline
		      when required.
		\item Worked extensively with the Stripe API and contributed to the migration from a legacy
		      billing platform. Required a near even split of frontend and backend
		      tasks. Code refactoring and unit testing using a combination of modern frameworks
		      (Mocha, Chai.js, Jest).
		\item Experience working with Elasticsearch for full text search of unstructured data,
		      Apache Cassandra for storage of semi-structured data, and MySQL (MariaDB) for structured data.
		      Achieved an understanding of the purpose of each of these data stores and where that technology may be
		      utilized in a single application.
	\end{itemize}

	\normalsize{\section{FliteX}}

	FliteX is an early stage startup aiming to be a major disruptor of the airline business. Using modern
	web technologies and data freely available through federal initiatives they are developing commercial
	flight route optimization that fits the SaaS model.

	\begin{tabular}{p{3in} r} % setup 2 columns, first
		% is 3 inches wide
		Full Stack Developer - \href{https://flitex.net/}{\textcolor{blue}{FliteX}}, Oshawa, ON & March 2020 - June 2020
	\end{tabular}
	\begin{itemize} % \item[] prevents a bullet from appearing
		\item Experienced the atmosphere at an early stage startup. Exposure to contract and freelance
		      work under intense time pressure and constraints. Garage mentality, prototyping, and iteration
		      on a tight schedule.
		\item Prototyped a map based SPA used for flight route optimization. Designed a 3-tier
		      web application consisting of an Angular frontend web application, Python API, and PostgreSQL
		      data layer.
		\item Ported MATLAB to Python (numpy, scipy). Assisted team members in translating purely mathematical equations from recently published academic research into Python code.
	\end{itemize}

	\normalsize{\section{Wysdom AI}}

	Wysdom AI is a late stage startup and artificial intelligence company offering virtual assistant software
	via a SaaS platform. The Wysdom AI chatbot product was initially designed to service the needs of
	large telecoms. As a result they were able to sign a number of big name clients in this space and have
	since been expanding their product's capabilities.

	\begin{tabular}{p{3in} r} % setup 2 columns, first
		% is 3 inches wide
		AI Automation Specialist - \href{https://wysdom.ai}{\textcolor{blue}{Wysdom AI}}, Richmond Hill, ON & June 2019 - March 2020
	\end{tabular}
	\begin{itemize} % \item[] prevents a bullet from appearing
		\item Hired as AI Application Specialist, promoted to AI Automation Specialist. Initially
		      excelling at the scripting/testing aspect of Application Specialist, was moved to
		      Automation Specialist where tasks were exclusively related to programming (Python).
		\item Developed web based business process automation tools and applications. Designed a 3-tier
		      web application consisting of an Angular frontend web application, Python API, and PostgreSQL
		      data layer. This application implemented an asynchronous task queue (Celery) to take user input
		      in the form of CSV files and execute testing of that data outside the regular request/response cycle.
		      When the task was complete the user would receive an email with the results of their test run.
		\item Contributed to the development of a prototype data pipeline which used audio filters
		      (FFmpeg) to manipulate mp3 formatted data. The data was
		      encoded and sent to a third party (Google STT API) for transcription.
		      Finally the transcribed data was classified using the in-house chat bot product,
		      proving the concept of re-purposing the text engine for conversational IVR.

	\end{itemize}
	\section{\textcolor{NavyBlue}{SKILLS}}
	\begin{multicols}{3}
		\begin{itemize}
			\item HTML
			\item CSS
			\item JavaScript
			\item TypeScript
			\item Node.js
			\item Angular 2+
			\item AngularJS
			\item connect
			\item express
			\item Python
			\item Go
			\item Rust
			\item MySQL
			\item PostgreSQL
			\item Cassandra
			\item MongoDB
			\item AWS
			\item GCP
			\item Git
			\item Agile
			\item CI/CD
		\end{itemize}
	\end{multicols}

	\section{\textcolor{NavyBlue}{CERTIFICATIONS}}
	\begin{itemize} % \item[] prevents a bullet from appearing
		\item OpenJS Node.js Services Developer, \textit{JSNAD}, Awarded April 2022, Expires April 2025,
					\href{https://www.youracclaim.com/badges/d17570bd-2145-4cc2-9645-673fc3f6947e}{\textcolor{blue}{Verify}}

		\item OpenJS Node.js Application Developer, \textit{JSNAD}, Awarded June 2021, Expires June 2024,
		      \href{https://www.youracclaim.com/badges/76bcd62c-af5b-4957-b9ef-533403369d8d}{\textcolor{blue}{Verify}}

		\item AWS Certified Solutions Architect (Associate), \textit{SAA-C02} Awarded November 2020, Expires November 2023
		      \href{https://www.youracclaim.com/badges/4b572dd0-85e9-45f5-90f8-90a68cd3399f}{\textcolor{blue}{Verify}}

		\item AWS Certified Cloud Practitioner, \textit{CLF-C01}, Awarded September 2020, Expires September 2023
		      \href{https://www.youracclaim.com/badges/48063b2f-6f7f-4b6c-a040-5c42393c4bc0}{\textcolor{blue}{Verify}}


		\item Certified Associate in Python Programming, \textit{PCAP-31-02}, \\
		      Awarded September 2020 \href{https://www.youracclaim.com/badges/bfd6aae6-1ab4-461b-8a62-f25cfb0bd29d}{\textcolor{blue}{Verify}}

	\end{itemize}

	\section{\textcolor{NavyBlue}{PROJECTS}}
	\normalsize{\section{Web App}}
	Map Application - (see \href{https://tripsultant.com}{\textcolor{blue}{\url{https://tripsultant.com}}}) - This work is an excellent example of a web application
	designed using a microservice architecture, containerization and a reactive frontend framework. This application is deployed in the
	cloud via an automated CI/CD pipeline using GitHub Actions. The frontend utilizes Angular 12 and Redux for state management. Microservices
	are implemented in Golang and JavaScript.
	\normalsize{\section{CLI Tool}}
	RandCSV - A simple Python command line utility that can be used to generate random CSV files.
	As an additional feature, values are generated using Python's built-in cryptographically strong random number generator. 
	This work serves as an example of a well documented Python CLI utility, 
	use of Object Oriented Programming, and Python's open source ecosystem. See it on \href{https://github.com/scriptloom/randcsv}
	{\textcolor{black}{\textcolor{blue}{GitHub}}}. See it on \href{https://pypi.org/project/randcsv/}
	{\textcolor{black}{\textcolor{blue}{PyPI}}}. See it on \href{https://randcsv.readthedocs.io/en/latest/}
	{\textcolor{black}{\textcolor{blue}{Read the Docs}}}.
	\normalsize{\section{Data \& AI}}
	Text Classifier - Personal Python project for easily creating text classification models. This work is an excellent example of transfer learning using \href{https://www.tensorflow.org/}{\textcolor{blue}{TensorFlow}}, where \href{https://arxiv.org/abs/1810.04805}{\textcolor{blue}{Google's BERT}} is fine tuned to produce high quality NLP models. If available, a system GPU will be utilized to decrease training execution time. See it on \href{https://github.com/jameone/woodgate}
	{\textcolor{black}{\textcolor{blue}{GitHub}}}.

	\section{\textcolor{NavyBlue}{LEADERSHIP}}
	\begin{itemize} \itemsep -2pt % reduce space between items
		\item \href{https://teamwaterloop.ca/}{\textcolor{blue}{Waterloop}} - Team Leader Magnetic Wheel. Managed the team responsible for the design of the magnetic wheel component. Competed in the SpaceX \href{https://en.wikipedia.org/wiki/Hyperloop_pod_competition}{\textcolor{blue}{Hyperloop Pod Competition}} 2017.
		\item \href{https://www.oelccaso.com/}{\textcolor{blue}{OELC}} Participant - Selected to attend Ontario Educational Leadership Camp.
	\end{itemize}

	\section{\textcolor{NavyBlue}{PUBLICATIONS}}
	\begin{itemize}
		\item \href{https://www.nrcresearchpress.com/doi/abs/10.1139/cjp-2017-0089?journalCode=cjp#.X3Z1_GhKiUk}{\textcolor{blue}{Approaching special relativity in complex time}}, Can. J. Phys., \textbf{95(10)} (2017) 923-926., Mathematical/theoretical physics, logic, set theory, and algebra
	\end{itemize}

	\section{\textcolor{NavyBlue}{AWARDS}}
	\begin{itemize}
		\item 	\href{https://www.cemc.uwaterloo.ca/contests/pcf.html}{\textcolor{blue}{Pascal Mathematics Contest}}, School champion, $25^{th}$ percentile.
	\end{itemize}
	% \section{\textcolor{NavyBlue}{REFERENCES}}
	% \begin{itemize}
	% 	\item \href{mailto:nora.rodriguez@wysdom.ai}{\textcolor{blue}{Nora Rodriguez}} - HR, Wysdom.AI \\
	% 	      {\it References are intended for employment records only.}
	% \end{itemize}
\end{resume}
\end{document}
